Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-11-25 Scripts/Initial_Analysis.Rmd
misc

spi_map <-  ggplot(spi_toe_map_data) +
  geom_sf(
    aes(
      fill = reverse #original map
      # fill = value
    ),
    color =  "white",
    size = 0.1
  ) +
  # Inlcude the participation of species
  geom_sf(data = spi_map_part,
          # aes(fill = participation+2000), #original map
          aes(fill = participation, 
              color = participation),
          # color =  "white",
          size = 0.1
  ) +
  # grey maps
  geom_sf(data = spi_no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
  geom_sf(data = spi_no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
  coord_sf(xlim = c(9500000,1000000),ylim = c(-3500000, 1900000)) + 
  facet_wrap(~tresh) +
  scale_colour_viridis("",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       # labels = c("","","","",""),
                       direction = 1
  ) +
  scale_fill_viridis("",
                     limits = c(2000,2100),
                     breaks = seq(2000,2100,25),
                     # labels = c("","","","",""),
                     direction = 1
  ) +
  scale_x_continuous(limits = c(-120,180),
                     breaks = c(-120,180)
                     # labels =c("a","b")
                     ) + 
  my_ggtheme_m(map_type = "regional",leg_pos = "bottom") +
  theme(legend.key.width = unit(3, "line"))

ggsave("spi_map.png",
       spi_map,
       width = 8,
       height = 6)
```

>>>>

spi_map <-  ggplot(spi_toe_map_data) +
  geom_sf(
    aes(
      fill = reverse #original map
      # fill = value
    ),
    color =  "white",
    size = 0.1
  ) +
  # Inlcude the participation of species
  geom_sf(data = spi_map_part,
          # aes(fill = participation+2000), #original map
          aes(fill = participation, 
              color = participation),
          # color =  "white",
          size = 1
  ) +
  # grey maps
  geom_sf(data = spi_no_toe_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
  geom_sf(data = spi_no_toe_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
  coord_sf(xlim = c(9500000,1000000),ylim = c(-3500000, 1900000)) + 
  facet_wrap(~tresh) +
  scale_colour_viridis("",
                       limits = c(2000,2100),
                       breaks = seq(2000,2100,25),
                       # labels = c("","","","",""),
                       direction = 1
  ) +
  scale_fill_viridis("",
                     limits = c(2000,2100),
                     breaks = seq(2000,2100,25),
                     # labels = c("","","","",""),
                     direction = 1
  ) +
  scale_x_continuous(limits = c(-120,180),
                     breaks = c(-120,180)
                     # labels =c("a","b")
  ) + 
  my_ggtheme_m(map_type = "regional",leg_pos = "bottom") +
  theme(legend.key.width = unit(3, "line"))

ggsave(".Figures/spi_map_bf.png",
       spi_map,
       width = 8,
       height = 6)
```
